% Last updated: 5/21/2017

\documentclass[11pt,letterpaper]{article}

\include{pkgs}
\input{cmds}

\begin{document}

% Name, phone, email, address
{\bf\huge Jiyeon Lee} \vspace{1em}\\
\noindent\begin{tabular}[t]{@{}l}
%  Ph.D. Candidate \\
%  School of Computing, \\
%  Korea Advanced Institute of Science and Technology (KAIST)
%  Postdoc \\
%  School of AI Convergence, \\
%  Soongsil University
  Assistant Professor \\
  School of Computer Science and Engineering, \\
  Kyungpook National University
\end{tabular}
\hfill
\begin{tabular}[t]{r@{}}
\\
Email: \email{jiyeon@knu.ac.kr} \\
Web: \href{https://leejiy.github.io}{https://leejiy.github.io} \\
\end{tabular}

%
% Research Interests
%

\sectiontitle{Research Interests}
General Topics in Web Security and Privacy, Software Security, Cybercrime, Side-channel attacks

%
% Education
%

\sectiontitle{Education}
\begin{envtime}{Korea Advanced Institute of Science and Technology (KAIST)}{Mar. 2014 -- Aug. 2021}
	\item Ph.D. in School of Computing
	\item Thesis: Security Defects and Client-side Countermeasures on Emerging Web Technologies
	\item Advisor: Insik Shin
\end{envtime}

\begin{envtime}{Korea Advanced Institute of Science and Technology (KAIST)}{Feb. 2012 -- Feb. 2014}
	\item M.S. in School of Computing
	\item Thesis: Thread-level Priority Assignment in Global Multiprocessor Scheduling for Parallel Tasks
	\item Advisor: Insik Shin
\end{envtime}

\begin{envtime}{Dankook University}{Mar. 2007 -- Feb. 2012}
	\item B.S. in Computer Science
\end{envtime}


\sectiontitle{Work Experience}
\begin{envtime}[South Korea]{Assistant, Kyungpook National University}{Mar. 2023 -- Current}
	\item School of Computer Science and Engineering
\end{envtime}
\begin{envtime}[South Korea]{Postdoc Researcher, MISYS Lab, Soongsil Univ.}{Sep. 2021 -- Feb. 2023}
	\item Advisor: Kilho Lee
	\item Dependable Autonomous Vehicles, WebVR Side-channel Attacks
\end{envtime}
%\begin{envtime}[South Korea]{Research Director, WISET Research Project}{Apr. 2020 -- Oct. 2020}
%	\item WebVR Ad Service
%\end{envtime}
\begin{envtime}[China]{Research Intern, Microsoft Research Asia}{Apr. 2019 -- Jun. 2019}
	\item Mentor:  Yunxin Liu in Intelligent Cloud and Edge Group
	\item Edge Intelligence
	%	\item VR Side-channel Attacks
\end{envtime}
%\begin{envtime}[South Korea]{Research Intern, Embedded System Lab, Dankook Univ.}{Dec. 2010 -- Jan. 2012}
%	\item Advisor: Jongmoo Choi
%	\item I/O Scheduling for Virtualization, Massive MLC SSD Project
%\end{envtime}



%
% Publications
%

\sectiontitle{Publications}
\subsectiontitle{International publications}{}

\begin{enumerate}



		\item \textbf{Tracking WebVR User Activities through Hand Motions: An Attack Perspective} \\
	\begin{small}
		\textbf{Jiyeon Lee}\\ 
	IEICE Transactions on Information and Systems, Vol. E107-D, No. 8, pp.1089-1092, Aug. 2024
	\end{small}

		\item \textbf{Data-Similarity-based IoT Node Selection for UAV Trajectory Optimization} \\
	\begin{small}
		Haoran Mei, Muhammad Fawad Khan, Limei Peng, Byungchul Tak, \textbf{Jiyeon Lee},  Pin-Han Ho\\ 
		Elsevier Computers and Electrical Engineering, Vol. 112, Dec. 2023
	\end{small}

		\item \textbf{VRKeyLogger: Virtual Keystroke Inference Attack via Eavesdropping Controller Usage Pattern in WebVR} \\
	\begin{small}
		\textbf{Jiyeon Lee}, Hyosu Kim, Kilho Lee \\ 
		Elsevier Computers \& Security, Vol. 134, Nov. 2023
	\end{small}
	
		\item \textbf{Spy in Your Eye: Spycam Attack via Open-Sided Mobile VR Device} \\
	\begin{small}
		\textbf{Jiyeon Lee}, Kilho Lee \\ 
		IEICE TRANSACTIONS on Information and Systems, Vol.E105-D, No.10, pp.1817-1820, Oct. 2022
	\end{small}
	
		\item \textbf{Exploiting Missing Value Patterns for a Backdoor Attack on Machine Learning Models of Electronic Health Records: Development and Validation Study} \\
	\begin{small}
		Byunggill Joe, Yonghyeon Park (co-first), Jihun Hamm, Insik Shin, \textbf{Jiyeon Lee} \\ 
JMIR Medical Informatics, Vol. 10, No. 8, Aug. 2022
	\end{small}
	
	\item \textbf{AdCube: WebVR Ad Fraud and Practical Confinement of Third-Party Ads} \\
	\begin{small}
		Hyunjoo Lee, \textbf{Jiyeon Lee (co-first)}, Daejun Kim, Suman Jana, Insik Shin, Sooel Son \\ 
		Proceedings of the 30th USENIX Security Symposium (Security 2021), Virtual, Aug. 2021
%		\textcolor{blue}{\textbf{*BK21 Excellence Conference}}
	\end{small}

	\item \textbf{CanvasMirror: Secure Integration of Third-Party Library in WebVR Environment} \\
	\begin{small}
		\textbf{Jiyeon Lee}\\ 
		Doctoral Forum of 50th IEEE/IFIP Conference on Dependable Systems and Networks (DSN 2020), Virtual, Jun. 2020
	\end{small}

	\item \textbf{Pride and Prejudice in Progressive Web Apps: Abusing Native App-like Features in Web Applications} \\
	\begin{small}
		\textbf{Jiyeon Lee}, Hayeon Kim, Junghwan Park, Insik Shin, Sooel Son\\ 
		Proceedings of the 25th ACM Conference on Computer and Communications Security (CCS 2018), Toronto, Canada, Oct. 2018
%		\textcolor{blue}{\textbf{*BK21 Excellence Conference}}
	\end{small}

	\item \textbf{Global EDF Schedulability Analysis for Parallel Tasks on Multi-core Platforms} \\
	\begin{small}
		Hoon Sung Chwa, Jinkyu Lee, \textbf{Jiyeon Lee}, Kieu-My Phan, Arvind Easwaran, Insik Shin\\ 
		IEEE Transactions on Parallel \& Distributed Systems (TPDS), Vol. 28, No. 5, pp.1331-1345, May. 2017
	\end{small}

	\item \textbf{Thread-level Priority Assignment in Global Multiprocessor Scheduling for DAG Tasks} \\
	\begin{small}
		\textbf{Jiyeon Lee}, Hoon Sung Chwa, Jinkyu Lee, Insik Shin\\ 
		Journal of Systems and Software (JSS), Vol. 113, pp. 246-256, Mar. 2016
	\end{small}

	\item \textbf{MC-Fluid: Fluid Model-based Mixed-Criticality Scheduling on Multiprocessors (Best Paper Runner-up Award)} \\
	\begin{small}
		Jaewoo Lee, Kieu-My Phan, Xiaozhe Gu, \textbf{Jiyeon Lee}, Arvind Easwaran, Insik Shin, Insup Lee\\ 
		Proceedings of the 35th IEEE Real-Time Systems Symposium (RTSS 2014), Rome, Italy, Dec. 2014
%		\textcolor{blue}{\textbf{*BK21 Excellence Conference}}
	\end{small}

	\item \textbf{Real-time Audio Coordination Framework for Immersive Sound Reproduction} \\
	\begin{small}
		Hyosu Kim, \textbf{Jiyeon Lee}, Hwidong Bae, Insik Shin\\ 
		Demo session at the 35th IEEE Real-Time Systems Symposium (RTSS@Work 2014), Rome, Italy, Dec. 2014
	\end{small}

	\item \textbf{Mobile Maestro: Enabling Immersive Multi-Speaker Audio Applications on Commodity Mobile Devices} \\
	\begin{small}
		Hyosu Kim, SangJeong Lee, Jung-Woo Choi, Hwidong Bae, \textbf{Jiyeon Lee}, Junehwa Song, Insik Shin\\ 
		Proceedings of the 16th ACM International Conference on Ubiquitous Computing (UBiComp 2014), Seattle, WA, US, Sep. 2014
%		\textcolor{blue}{\textbf{*BK21 Excellence Conference}}
	\end{small}

\end{enumerate}

\subsectiontitle{Domestic Publications}{}
\begin{enumerate}

	\item \textbf{Analysis of Security Vulnerabilities and Personal Information Exposure Risks in Overleaf} \\
	\begin{small}
		Suzi Kim, \textbf{Jiyeon Lee}\\ 
		Journal of The Korea Society of Computer and Information, Vol. 29, No. 7, pp.109-115, Jul. 2024
	\end{small}

	\item \textbf{Metadata-based Backdoor Attack on Medical Neural Networks} \\
	\begin{small}
		Yonghyeon Park, Byunggil Joe, \textbf{Jiyeon Lee}, Minwoo Jeong, Insik Shin\\ 
		Workshop on Dependable and Secure Computing, Jeju, South Korea, Aug. 2021
	\end{small}

	\item \textbf{Parallel Task Multi-core Scheduling for Real-Time Cyber-Physical Systems} \\
	\begin{small}
		\textbf{Jiyeon Lee}, Insik Shin\\ 
		Telecommunications Review, Aug. 2015
	\end{small}
	
	\item \textbf{GPGPU Parallelization Techniques for Redundancy Elimination Algorithm (Best Paper Award)} \\
	\begin{small}
		Byunggil Joe, Dae R. Jeong, \textbf{Jiyeon Lee}, Insik Shin\\ 
		Korean Institute of Information Scientists and Engineers (KIISE 2014), Pyeongchang, South Korea, Dec. 2014
	\end{small}

	\item \textbf{GPU-SPARC: Accelerating Parallelism in Multi-GPU Real-Time Systems} \\
	\begin{small}
		Wookhyun Han, Hwidong Bae, Hyosu Kim, \textbf{Jiyeon Lee}, Insik Shin\\ 
		Technical Report, School of Computing, KAIST, CS-TR-2014-391, Aug. 2014
	\end{small}
	
	\item \textbf{RT-SDN: Adaptive Routing and Priority Ordering for Software-Defined Real-Time Networking} \\
	\begin{small}
		Sangeun Oh, \textbf{Jiyeon Lee}, Kilho Lee, Insik Shin\\ 
		Technical Report, School of Computing, KAIST, CS-TR-2014-387, Aug. 2014
	\end{small}
	
	\item \textbf{A Survey on Real-time Support for Mixed-criticality Cyber-Physical Systems} \\
	\begin{small}
		Jaewoo Lee, \textbf{Jiyeon Lee}, Insik Shin\\ 
		Korea Information Science Society, Vol. 31, No. 12, Dec. 2013
	\end{small}
	
	\item \textbf{Optimal Priority Assignment for Parallel Tasks under Fixed Priority Scheduling in Real-time Systems (Best Paper Award)} \\
	\begin{small}
		\textbf{Jiyeon Lee}, Hoon Sung Chwa, Insik Shin\\ 
		Korean Institute of Information Scientists and Engineers (KIISE 2013), Jeju, South Korea, Nov. 2013
	\end{small}
\end{enumerate}

%
% Work Experience
%


% Honors & Awards
\sectiontitle{Honors \& Awards}

%\subsectiontitle[NRF]{Post-Doc Domestic Training Fellowship}{2022 -- 2023} \\
\subsectiontitle[The 28th IEEE Network and Distributed System Security Symposium]{Student Grant}{Feb. 2021} \\
\subsectiontitle[]{EECS Rising Stars in Korea}{Sep. 2020} \\
\subsectiontitle[WISET]{STEM Research Team Project Fellowship}{2020} \\
\subsectiontitle[NAVER Corporation]{Ph.D. Fellowship}{Nov. 2019} \\
\subsectiontitle[Samsung Internet push notification origin missing]{Bug Bounty}{Jan. 2019} \\
\subsectiontitle[D’LIVE]{KAIST-D’LIVE Research \& Presentation Scholarship}{Dec. 2018} \\
\subsectiontitle[The 25th ACM Computer and Communications Security]{Student Travel Grant}{Oct. 2018} \\
\subsectiontitle[The 41st Korean Institute of Information Scientists and Engineers ]{Best Paper Award}{Jan. 2015} \\
\subsectiontitle[The 35th IEEE Real-Time Systems Symposium ]{Best Paper Runner-up}{Dec. 2014} \\
\subsectiontitle[The 40th Korean Institute of Information Scientists and Engineers ]{Best Paper Award}{Nov. 2013} \\
\subsectiontitle[Dankook University]{Excellent Records Awards}{2010 -- 2011}




\sectiontitle{Research Experience as a Principal Investigator}
\begin{envtime}[National Research Foundation of Korea]{First Research in life time}{Sep. 2023 -- Feb.2026}
	\item Title: Security Research on XR for Safe Metaverse
	\item Amount: 72,450,000 won
\end{envtime}
\begin{envtime}[Kyungpook National University]{New Faculty Startup Fund}{Mar. 2023 -- Feb. 2024}
	\item Title: Study on Security Risks of Motion-Based Input in VR
	\item Amount: 9,000,000 won
\end{envtime}
\begin{envtime}[National Research Foundation of Korea]{Post-Doc Domestic Training}{Sep. 2022 -- Feb. 2023}
	\item Title: Study of new security threats from motion-based input in AR/VR
	\item Amount: 60,000,000 won
\end{envtime}



% Imvited Talks
%\sectiontitle{Invited Talks}
%
%\begin{envtime}[]{Up-and-coming Doctor Session of KIISE Women Workshop}{Oct. 2020}
%	\item ``A Study on the Detection and Defense of Vulnerabilities Due to Emerging Web Technology''
%\end{envtime}
%\begin{envtime}[]{EECS Rising Stars in Korea}{Sep. 2020}
%	\item ``A Study on the Detection and Defense of Vulnerabilities Due to Emerging Web Technology''
%\end{envtime}
%\begin{envtime}[]{Doctoral Forum of DSN}{Jun. 2020}
%	\item ``CanvasMirror: Secure Integration of Third-Party Library in WebVR Environment''
%\end{envtime}
%\begin{envtime}[]{Doctoral Forum of KIISE}{Dec. 2019}
%	\item ``A Study on the Detection and Defense of Vulnerabilities Due to Emerging Web Technology''
%\end{envtime}
%\begin{envtime}[]{CCS}{Oct. 2018}
%	\item ``Pride and Prejudice in Progressive Web Apps: Abusing Native App-like Features in Web Applications''
%\end{envtime}
%\begin{envtime}[]{RTSS@Work}{Dec. 2014}
%	\item ``Real-time Audio Coordination Framework for Immersive Sound Reproduction''
%\end{envtime}


% Teaching Experience
%\sectiontitle{Professional Activities}
%\begin{envtime}[]{Teaching Assistant or Preceptor}{}
%	\item{Operating Systems and Lab. (CS330), School of Computing, KAIST}{, 2012 -- 2015}
%	\item{Real-time Systems (CS634), School of Computing, KAIST}{, Fall 2014}
%	\item{Counseling Assistant, School of Computing, KAIST}{, Spring 2013, Spring 2016, Spring 2018}
%	\item{Introduction to Data Science in Python, Elice academy}{, Feb. 2018 -- Mar. 2018}
%%	\item{Computing Security (SEP543), School of Computing, KAIST}{, Summer 2021}
%\end{envtime}
%
%
%\begin{envtime}[]{External Reviewer}{}
%	\item{ACM ASIA Conference on Computer and Communications Security (ASIACCS)}{, 2022}
%	\item{Emerging Technologies and Factory Automation (ETFA)}{, 2015}
%	\item{Euromicro Conference on Real-Time Systems (ECRTS)}{, 2012, 2014 - 2015}
%	\item{IEEE Real-Time and Embedded Technology and Applications Symposium (RTAS)}{, 2013 - 2014}
%	\item{IEEE Real-Time Systems Symposium (RTSS)}{, 2012 - 2014}
%	\item{Real-Time Computing Systems and Applications (RTCSA)}{, 2013}
%	\item{ACM SIGBED International Conference on Embedded Software (EMSOFT)}{, 2012}
%\end{envtime}



\end{document}
